Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-26 main.Rmd
index starts from 0 for figure 1

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="The time domain distributed as linear granularities hours, days, weeks and months. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating."}
knitr::include_graphics("Figs/linear-arr.png")
```

>>>>

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="The time domain distributed as linear granularities hours, days, weeks and months. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating."}
knitr::include_graphics("Figs/linear-arr1.png")
```
